---
title: "Project Sleepy"
author: "Justin C, Lauryn E, Samuel S, Zerong W"
date: "11/14/2022"
output: html_document
---

```{r pressure, echo=FALSE}
source("../source/ChartForQuestion1.R")
plot(chart1)
min_study_hr <- find_min_studyhr()
```

This bar chart is in correspodance to our first research question *"Does longer study hours correspond to a higher GPA?"* This visualization was included in order to find a correspondence between a person's GPA and the time they spend studying. According to our findings, it appears that time spent studying has no real correlation to school performance GPA-wise. For example, the minimum time someone has spent studying is `r min_study_hr`, but the students with that amount of study time on average do not have the lowest GPAs.

```{r, echo=FALSE}
source("../source/ChartForQuestion3.R")
plot(chart3)
max_avg_sleep <- find_max_avg_sleep()
```

This bar chart is in correspondence to our third research question: *"How does sleep duration and quality impact university students’ academic performance?"* This visualization was included to display the cumulative GPA of students in correlation to the average amount of sleep they would get. We observed that as the amount of sleep a student got decreased, so did their cumulative GPA. A notable observation is that even solely considering the highest GPAs, the average amount of sleep a student got was only `r max_avg_sleep` hours, which is below the widely-recommended **8** hours of sleep.