---
title: "Project Sleepy"
author: "Justin C, Lauryn E, Samuel S, Zerong W"
date: "11/14/2022"
output: html_document
---

<<<<<<< HEAD
=======
```{r source, echo=FALSE}
source("../source/summary_info.R")
```
## What is this report for?

As our title suggests, this is a report on the impact of sleep on college students. The reason we decided to conduct the analysis is that this is exactly what concerns us as college students, which is to know how sleep affects the lives of college students, especially in terms of academic performance. We found our first dataset through the Kaggle, this dataset focuses on the relationship between student academic performance and sleep duration, we found that this data set has `r get_num_var_3()` columns (variables) corresponding to `r get_num_obs_3()` observations (rows). According to this dataset, the average sleep time of students with GPA between 3.5 and 4.0 is **`r find_avg_sleep()`** hours. From this we can see that students with high GPAs tend to sleep less than the recommended 8 hours of sleep. In our second dataset, it has `r get_num_var_2()` columns (variables) corresponding to `r get_num_obs_2()` observations (rows). This dataset focuses on relationship between sleep duration and fear of COVID-19 during the pandemic. According to this dataset, we found that Bangladeshi university students slept an average of **`r find_avg_sleep_2()`** hours during the pandemic when fear of COVID-19 was high. From this we can see that the fear of Covid-19 does not seem to affect the sleep duration.

## Table


## Plots
### Chart 1
>>>>>>> refs/remotes/origin/main
```{r pressure, echo=FALSE}
source("../source/ChartForQuestion1.R")
plot(chart1)
min_study_hr <- find_min_studyhr()
```

This bar chart is in correspodance to our first research question *"Does longer duration of studying lead to a higher GPA"* This visualization was included in order to find a correspondence between a person's GPA and the time they spend studying. According to our findings, it appears that time spent studying has no real correlation to school performance GPA-wise. For example, the minimum time someone has spent studying is `r min_study_hr`, but the students with that amount of study time on average do not have the lowest GPAs.

### Chart 2
```{r, echo=FALSE}
source("../source/ChartForQuestion2.R")
plot(chart2)
max_avg_fear <- find_max_avg_fear()
```
This chart is a visualization of our second research question, *"What is the relationship between sleep duration and fear of COVID-19 for university students for online learning during the COVID-19 pandemic?"* This visualization was crafted to find this relationship between average time asleep and fear of the COVID-19 virus. We can see from our findings that there is no clear relationships between fear and COVID-19. We can slightly see that as the fear of COVID-19 increases, the line increases as well, indicating that the average hours of sleep increase. Although, the data appears to be extremely scattered from our smoothed line, with a significant amount of outliars. This leads us to believe that there is no significant relationship between these two variables

### Chart 3
```{r, echo=FALSE}
source("../source/ChartForQuestion3.R")
plot(chart3)
max_avg_sleep <- find_max_avg_sleep()
```

This bar chart is in correspondence to our third research question: *"How does sleep duration and quality impact university students’ academic performance?"* This visualization was included to display the cumulative GPA of students in correlation to the average amount of sleep they would get. We observed that as the amount of sleep a student got decreased, so did their cumulative GPA. A notable observation is that even solely considering the highest GPAs, the average amount of sleep a student got was only `r max_avg_sleep` hours, which is below the widely-recommended **8** hours of sleep.